---
title: "R Objects, Workflow, and Functions"
format: pdf
editor: visual
---

# Vectors

Create a vector.

```{r}
set.seed(42)
my_unif <- runif(30)
is.vector(my_unif)
```

Note: set.seed() will ensure we get the same results if we run the random generator again.

Subset that object.

```{r}
my_unif[1:10]
```

```{r}
my_unif[c(1:3, 15:17)]
```

Sort the vector.

```{r}
sort(my_unif)
```

Create a vector with strings in it.

```{r}
char_vec <- c('Kim', 'Alice', 'Dylan', 'Luna', 'Stella')
sort(char_vec)
```

Note: If there is a combination of numberical and character elements, sort function will sort by numbers first.

# Data Frames

```{r}
data(trees)
trees
str(trees)
```

Subset a column.

```{r}
trees$Height
```

Get attributes from the data frame.

```{r}
attributes(trees)
names(trees)
colnames(trees)[2:3]
```

# Lists

Investigating data frame from before.

```{r}
is.list(trees)
```

```{r}
is.data.frame(trees)
```

Can subset as a list.

```{r}
trees[1]
```

```{r}
trees[[1]]
```

```{r}
trees[1:2]
```

```{r}
trees[[2]]
```

Look at linear model fit.

```{r}
fit <- lm(Volume ~ Height + Girth, data = trees)
```

Look at structure but restrict info.

```{r}
str(fit, max.level=1)
```

Some helper functions exist.

```{r}
fit$coefficients
coef(fit)
```

```{r}
fit$residuals
residuals(fit)
```
